---
title: "Results food data clustering DEL"
output:
  html_notebook: default
  pdf_document: default
---

```{r loadlib, include=FALSE}
library(FactoMineR)
library(factoextra)
library(arsenal)
library(Rtsne)
library(plotly)
library(tidyverse)
```

# All Data clusters (Deep learning, DEL (Deep Embedding Clustering layer))

```{r}
DEC_Embedding = read.csv('/Users/xbasra/Documents/Data/Clustering_Food_Alergies/Intermediate/CsvData_Output/DEC_Embedding.csv')
head(DEC_Embedding)
```

```{r}
set.seed(10)
#tsne_converted_food_DEL <- Rtsne(X = EDL_Embedding ,perplexity= 200, is_distance = FALSE, check_duplicates = FALSE)
tsne_converted_food_DEC <- Rtsne(X = DEC_Embedding ,perplexity= 150, is_distance = FALSE, check_duplicates = FALSE)

tsne_converted_food_DEC <- tsne_converted_food_DEC$Y %>%
  data.frame() %>%
  setNames(c("X", "Y"))

tsne_converted_food_DEC$cl <- factor(resultft_DEL_all$cluster)
ggplot(tsne_converted_food_DEC, aes(x=X, y=Y, color=cl)) + geom_point()

#ggplot(aes(x = X, y = Y), data = tsne_converted_food_DEC)  + geom_point()
```

```{r}
tsne_converted_food_DEC_3d <- Rtsne(X = DEC_Embedding ,perplexity= 150, dims = 3, is_distance = FALSE, check_duplicates = FALSE)

tsne_converted_food_DEC_3d <- tsne_converted_food_DEC_3d$Y %>%
  data.frame() %>%
  setNames(c("X", "Y", "Z"))

tsne_converted_food_DEC_3d$cl <- factor(resultft_DEL_all$cluster)

p <- plot_ly(tsne_converted_food_DEC_3d, x = ~X, y = ~Y, z = ~Z, color = ~cl, colors = c('#BF382A', '#0C4B8E')) %>%
  add_markers() %>%
  layout(scene = list(xaxis = list(title = 'Dim1'),
                     yaxis = list(title = 'Dim2'),
                     zaxis = list(title = 'Dim3')))
p
```

```{r}
resultft_DEL_all <- read.csv('/Users/xbasra/Documents/Data/Clustering_Food_Alergies/Intermediate/CsvData_Output/resultft_DEL_all.csv')
# replacing the empty space "" values with no as done in the main analysis file
resultft_DEL_all$farmlive[resultft_DEL_all$farmlive == ""] <- NA
resultft_DEL_all <-  resultft_DEL_all %>% replace_na (list(farmlive = 'no'))
#tsne_converted_food$cl_DEL <- factor(resultft_DEL_all$cluster)
#ggplot(tsne_converted_food, aes(x=X, y=Y, color=cl_DEL)) + geom_point()
resultft_DEL_all$cluster <- as.factor(resultft_DEL_all$cluster)
```

```{r}
dist_plot_clust <-function(original_data, selected_variable){
  selected_variable <- enquo(selected_variable)
  ggplot(original_data, aes(UQ(selected_variable))) + geom_density(aes(fill = factor(cluster)), alpha=0.8) +
    labs(title = "Density plot",
         subtitle="sIgE_f1 of persons Grouped by Clusters",
         caption="Source: Source: results of Hierarchical clustering with tree-based distance and distance d1",
         x="sIgE_f1",
         fill="# Clusters")
} 
```

```{r}
dist_plot_clust(original_data = resultft_DEL_all, selected_variable = age)
```


### Density plot shoiwing the age distribution for each cluster
```{r}
resultft_DEL_all$cluster <- as.factor(resultft_DEL_all$cluster)

age_g <- ggplot(resultft_DEL_all, aes(sIgE_f3))
age_p <- age_g + geom_density(aes(fill=factor(cluster)), alpha=0.8) +
    labs(title="Density plot",
         subtitle="sIgE_f1 of persons Grouped by Clusters",
         caption="Source: Source: results of Hierarchical clustering with tree-based distance and distance d1",
         x="sIgE_f1",
         fill="# Clusters")

ggplotly(age_p)
```


```{r}
g <- ggplot(resultft_DEL_all, aes(bmi2)) + scale_fill_brewer(palette = "Spectral")
s <- g + geom_histogram(aes(fill=factor(cluster)), 
                   bins=5, 
                   col="black", 
                   size=.1) +   # change number of bins
  labs(title="Histogram with Fixed Bins", 
       subtitle="Age across different clusters",
       x="Age",
         fill="# Clusters") 

ggplotly(s)
```

```{r}
table_uft_DEL_all <- tableby(cluster ~ ., data = as.list(resultft_DEL_all))
summary(table_uft_DEL_all, title = "Charachtaristcs of Clusters")
# adding the id variable 
#result_food_uft_DEL_k$ID <- food_data_id$ID 
#write.csv(result_food_uft_DEL_k, "/Users/xbasra/Documents/Data/Clustering_Food_Alergies/CsvData/result_food_uft_DEL_k.csv")
```



## Charachtiristic Analysis
```{r, warning=FALSE}
resultft_DEL_all$cluster <- as.factor(resultft_DEL_all$cluster)
catdes(resultft_DEL_all, 16)
```



# Random Data clusters with DEL (Deep Embedding Clustering layer)

```{r}
#result_rand_uft_DEL_k <- read.csv("/Users/xbasra/Documents/Data/Clustering_Food_Alergies/Intermediate/CsvData_Output/result_rand_food_uft_DEL_k.csv")
result_rand_uft_DEL_k <- read.csv("/Users/xbasra/Documents/Data/Clustering_Food_Alergies/Intermediate/CsvData_Output/result_rand_uft_DEL_k.csv")
result_rand_uft_DEL_k$farmlive[result_rand_uft_DEL_k$farmlive == ""] <- NA
result_rand_uft_DEL_k <-  result_rand_uft_DEL_k %>% replace_na (list(farmlive = 'no'))
table_rand_uft_DEL_k <- tableby(cluster ~ ., data = as.list(result_rand_uft_DEL_k))
summary(table_rand_uft_DEL_k, title = "Charachtaristcs of Clusters")
# adding the id variable 
#result_food_uft_DEL_k$ID <- food_data_id$ID 
#write.csv(result_food_uft_DEL_k, "/Users/xbasra/Documents/Data/Clustering_Food_Alergies/CsvData/result_food_uft_DEL_k.csv")
```

## Charachtiristic Analysis
```{r, warning=FALSE}
result_rand_uft_DEL_k$cluster <- as.factor(result_rand_uft_DEL_k$cluster)
#result_food_uft_DEL_k <- result_food_uft_DEL_k[-c(1,2,20)]
catdes(result_rand_uft_DEL_k, 16)
```

# With asthma and Rhinitis Data clusters with DEL (Deep Embedding Clustering layer)

```{r}
result_as_rh_uft_DEL <- read.csv('/Users/xbasra/Documents/Data/Clustering_Food_Alergies/Intermediate/CsvData_Output/result_as_rh_uft_DEL.csv')
result_as_rh_uft_DEL$farmlive[result_as_rh_uft_DEL$farmlive == ""] <- NA
result_as_rh_uft_DEL <-  result_as_rh_uft_DEL %>% replace_na (list(farmlive = 'no'))
table_as_rh_uft_DEL <- tableby(cluster ~ ., data = as.list(result_as_rh_uft_DEL))
summary(table_as_rh_uft_DEL, title = "Charachtaristcs of Clusters")
# adding the id variable 
#result_food_uft_DEL_k$ID <- food_data_id$ID 
#write.csv(result_food_uft_DEL_k, "/Users/xbasra/Documents/Data/Clustering_Food_Alergies/CsvData/result_food_uft_DEL_k.csv")
```

## Charachtiristic Analysis
```{r, warning=FALSE}
result_as_rh_uft_DEL$cluster <- as.factor(result_as_rh_uft_DEL$cluster)
catdes(result_as_rh_uft_DEL, 16)
```


# Without asthma and Rhinitis Data clusters with DEL (Deep Embedding Clustering layer)

```{r}
result_no_as_rh_uft_DEL <- read.csv('/Users/xbasra/Documents/Data/Clustering_Food_Alergies/Intermediate/CsvData_Output/result_no_as_rh_uft_DEL.csv')
result_no_as_rh_uft_DEL$farmlive[result_no_as_rh_uft_DEL$farmlive == ""] <- NA
result_no_as_rh_uft_DEL <-  result_no_as_rh_uft_DEL %>% replace_na (list(farmlive = 'no'))
table_no_as_rh_uft_DEL <- tableby(cluster ~ ., data = as.list(result_no_as_rh_uft_DEL))
summary(table_no_as_rh_uft_DEL, title = "Charachtaristcs of Clusters")
# adding the id variable 
#result_food_uft_DEL_k$ID <- food_data_id$ID 
#write.csv(result_food_uft_DEL_k, "/Users/xbasra/Documents/Data/Clustering_Food_Alergies/CsvData/result_food_uft_DEL_k.csv")
```

## Charachtiristic Analysis
```{r, warning=FALSE}
result_no_as_rh_uft_DEL$cluster <- as.factor(result_no_as_rh_uft_DEL$cluster)
catdes(result_no_as_rh_uft_DEL, 16)
```




# adding the id varaible
```{r}
resultft_DEL_all$ID <- food_data_id$ID
result_rand_uft_DEL_k$ID <- rand_food_data_id$ID
result_as_rh_uft_DEL$ID <- as_ri_food_id$ID
result_no_as_rh_uft_DEL$ID <- no_as_ri_food_id$ID
write.csv(resultft_DEL_all,'/Users/xbasra/Documents/Data/Clustering_Food_Alergies/Results/CSVData/resultft_DEL_all_id.csv')
write.csv(result_rand_uft_DEL_k,'/Users/xbasra/Documents/Data/Clustering_Food_Alergies/Results/CSVData/result_rand_uft_DEL_k_id.csv')
write.csv(result_as_rh_uft_DEL,'/Users/xbasra/Documents/Data/Clustering_Food_Alergies/Results/CSVData/result_as_rh_uft_DEL_id.csv')
write.csv(result_no_as_rh_uft_DEL,'/Users/xbasra/Documents/Data/Clustering_Food_Alergies/Results/CSVData/result_no_as_rh_uft_DEL_id.csv')
```



















